---
title: "Class Markdown Example"
author: 
  - Allison Jones-Farmer
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: 
  html_document:
    code_folding: show
    df_print: paged
    number_sections: yes
    theme: cerulean
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      cache=TRUE,
                      out.width="100%",
                      warning=FALSE,
                      message=FALSE,
                      clean_cache=TRUE)
```

{r, echo =FALSE}
if(require(pacman)==0)
# Introduction


This is an `RMarkdown` document.  For more details on using `RMarkdown`, see <http://rmarkdown.rstudio.com>.  

Here is another great reference for `RMarkdown` <https://rstudio.com/wp-content/uploads/2015/03/rmarkdown-reference.pdf>

Here is the `RMarkdown` Cookbook:  <https://bookdown.org/yihui/rmarkdown-cookbook/font-color.html>




# Annotated Summary

## One number

```{r pressure,results='asis'}
pressure
paste("the mean pressure is ",round(mean(pressure$pressure), 2,"mm")
```
The standard deviation of pressure is 'r round(mean(pressure$pressure), 2)'mm.
## A table


```{r nameitsomething,results='asis'}

```


# Including Plots 

You can also embed plots, for example:

## Plotly 

```{r pressurePlot, echo=FALSE}

```

## Map

```{r fsbLoc, echo=FALSE}
datatable(pressure, caption="Table1.1")
```

For more details on organizing with tabset go here <https://bookdown.org/yihui/rmarkdown-cookbook/html-tabs.html>.

# Equations

You can include both inline and offset equations.

## Inline equations


## Offset equations


# References
